Cybercrime and Online Video Games

### 2019-12-13 paper/paper.tex
Fix header

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

>>>>

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[EECS349 F19]{CWRU EECS349 '19: Final Project}{December 13, 2019}{Cleveland, OH}
